The Galaxy Clustering Crisis in Abundance Matching

### 2017-05-01 paper/paper.tex
updates

(Sub-)haloes are found using the phase-space halo finder {\tt ROCKSTAR} \citep{Behroozi:2013cn, Behroozi:2013dz}, which uses adaptive, hierarchical refinement of friends-of-friends groups in six phase-space dimensions and one time dimension. As demonstrated in \cite{Knebe:2011jc, Knebe:2013bp}, this results in a very robust tracking of (sub-)haloes \citep[also see][]{vandenBosch:2014tl}. Haloes in this catalogue are defined to be spherical volumes centred on a local density peak (SO hereafter), such that the average density inside the sphere is $\bar{\rho}_{\rm h}(z) = \Delta_{\rm vir}(z)\rho_{\rm m}(z)$.  Here $\rho_{\rm m}(z) = \Omega_{\rm m}(z) \rho_{\rm crit}(z)$, where $\rho_{\rm crit}(z) = 3H(z)^2/8\pi G$ is the critical energy density of the Universe, and $\Delta_{\rm vir}(z)$ is given by a fitting function \citep{Bryan:1998cc}:
%
\begin{linenomath}
\begin{equation}
\Delta_{\rm vir}(z) = \left[ 18\pi^2 - 82\Omega_{\Lambda}(z) - 39\Omega_{\Lambda}^2(z) \right]\Omega_m^{-1}
\end{equation}
\end{linenomath}
%
For the Bolshoi cosmology, $\Delta_{\rm vir}(z=0)\simeq 360$.  The radius of each such sphere defines the virial radius $R_{\rm vir}$ of the halo, which is related to the mass of the halo via $M_{\rm vir} = (4/3)\pi R_{\rm vir}^3\bar{\rho}_{\rm h}$. Additionally, sub-haloes in this catalogue are distinct, self-bound structures whose centre is found within the virial radius of a more massive host-halo.  Additionally, for each (sub-)halo, the maximum circular velocity is defined as: $V_{\rm max} \equiv {\rm Max}[GM(<r)/r]$, where $M(<r)$ is the mass enclosed within a distance r of the (sub-)halo centre.

@@

To begin, we fit the $\langle M_* \rangle - V_{\rm peak}$ relation in the RV model with a function of the form:
%
\begin{linenomath}
\begin{equation}
\label{eq:smvp_relation}
\langle M_* | V_{\rm peak} \rangle = 2M_0\left(\frac{V_{\rm peak}}{V_0}\right)\left[\left(\frac{V_{\rm peak}}{V_0}\right)^{\alpha}+\left(\frac{V_{\rm peak}}{V_0}\right)^{\beta}\right]^{-1}
\end{equation}
\end{linenomath}
%
We perform a non-linear least squares fit to the mean stellar mass in 0.025 dex $V_{\rm peak}$ bins.  We find the parameters $\log(M_0/h^{-2}M_{\odot})=10.0 \pm 0.01$, $\log(V_0/{\rm km/s})=2.197 \pm 0.004$, $\alpha=-4.6 \pm 0.1$, and $\beta=-0.20 \pm 0.01$ provide an excellent fit.

As discussed, the RV model implies that galaxies grow along a fixed relation between stellar mass and $V_{\rm pealk}$, i.e. galaxy growth is tied to the growth of $V_{\rm peak}$ in haloes.  Accordingly, the average growth history of galaxies is dependent on the average potential well growth histories of haloes, $\langle V_{\rm peak} \rangle (z | V_{\rm peak, 0})$, \citep[PWGHs,][]{Bosch:2014cu}, and the form of the $\langle M_*\rangle - V_{\rm peak}$ relation, eq. \ref{eq:smvp_relation}.  We show the implied growth history of galaxies in the RV model in Fig. \ref{fig:mstar_of_z_rm} for haloes with different $V_{\rm peak}$ at z=0.0.  For comparison, we also show the stellar mass growth histories from M13, which depends on the average mass accretion histories (MAHs) of haloes, where halo mass has been converted to $V_{\rm peak}$ using eq. \ref{eq:vpeak} to place these histories on the same figure.  B13 and Y12 result in qualitatively similar growth histories as M13.

@@

\begin{figure}
    \includegraphics{figures/smhm_assem_bias.pdf}
    \caption{In the upper panel, we plot the SMHM relation for individual galaxies as points, colour-coded by the half mass scale, $a_{1/2}$.  The mean relation is plotted as a solid line with the $\pm 1\sigma$ scatter shown as dashed lines.  In the bottom panel, we show the strength of assembly bias, parametrized by the $\rho$ parameter.}
    \label{fig:assem_bias_smhm}
\end{figure}

@@

@@

@@

\section{Discussion}

Each of the modifications to SHAM considered in this paper increase the clustering signal by increasing the satellite fraction.  Adding orphan galaxies increases the number of satellites, but does not change the relation between halo mass and stellar mass.  The other two solutions considered here alter the SMHM relation for satellites by 1.) allowing satellites to grow after being accreted, and 2.) allowing galaxies which become satellites to grow more massive before accretion.  By increasing the stellar mass fraction of sub-haloes, the satellite fraction increases simply because the sub-halo fraction increases as halo mass decreases.

The tension between fitting the stellar mass function at multiple redshifts and galaxy clustering has been hinted at in many other works.  In \cite{Yang:2012ew}, when fitting galaxy clustering observations, or the conditional stellar mass function (CSMF), the data strong prefers more massive satellites and longer sub-halo survival times.  It is only when we apply this model (Y12) to dark matter simulations directly, that it becomes clear that there simply aren't enough extant sub-haloes.  \citep{Lim:2016ul} find a similar result, but instead of fitting to $w_p(r_p)$, they compare to the CSMF only.  Again, only models which allow for a significant orphan population can provide a good fit the the faint end of the CSMF, another indication that the true culprit in the clustering crisis is a lack of satellite galaxies.

Broadly, the usefulness of orphans when fitting galaxy clustering is well established.  \cite{Pujol:2017ua}, in a comparison of many galaxy formation models, find that only models with orphan galaxies are able to fit clustering observations on small scales.

{\bf [Effect of baryons on sub-haloes]}

{\bf [Methods to track sub-haloes that are robust to artificial merging/disruption]}

Most bound halo particle \citep{Hong:2016hv}.

{\bf [Assembly Bias]}
\citep{Zentner:2016tz} find significant evidence for assembly bias {\bf [is this still true?]} in low luminosity samples, exactly the regime where clustering is under-predicted.   
The assumptions in SHAM have been independently examined in the Eagle simulation by \cite{Matthee:2016vm}, who find that at fixed halo mass, the scatter in the SMHM relation is correlated with formation time.

{\bf [discussion of Vmax vs Mvir as indicators of stellar mass]}

Most studies which tout $V_{\rm max}$ as a superior halo property for SHAM do so when fitting galaxy clustering at z=0 \citep{Reddick:2013gi, Lehmann:2015vi}.  \cite{Matthee:2016vm} find that scatter is minimized in the $V_{\rm max}$-$M_*$ relation compared to the SMHM relation.

{\bf [Observational tests to distinguish between solutions proposed here]}

Differentiating between the solutions discussed in this work may prove to be difficult, especially if each plays some role.  Observations to constrain the SMHM relation for satellite galaxies are difficult.  \cite{Niemiec:2017ul} use weak lensing to examine the SMHM relation in cluster sub-haloes.

\section{Summary}

We have shown that there is no published SHAM model that simultaneously:
\begin{enumerate}
\item fits the stellar mass function as a function of redshift, $\phi(M_*,z)$,
\item fits the clustering of galaxies at z=0, $w_p(r_p)$,
\item and uses only identified, extant, sub-haloes in high resolution dark matter simulations.
\end{enumerate}
Models that fit galaxy clustering observations and are unable to reproduce the build of stellar mass in the Universe, and conversely, SHAM models which do reproduce the build up of stellar mass significantly under-predict galaxy clustering signals at small scales.  This tension presents a clustering ``crisis'' for abundance matching.

In this work, we explore five different SHAM models, focusing on the galaxy clustering predictions of each.  SHAM based on rank ordering (sub-)haloes by peak maximum circular velocity, $V_{\rm peak}$, (see RV model \S \ref{sec:rank_sham}) results in galaxy clustering that is strong enough to be consistent with measurements made using SDSS observations.  However, the RV model is not consistent with the growth of stellar mass as implied by previous studies.  Furthermore, there is no strong theoretical reason to assume stellar mass strongly correlates with $V_{\rm peak}$ over other more natural measures of halo mass.

On the other hand, all published SHAM models based on peak halo mass, $M_{\rm peak}$, (RM, M13, B13, and Y12 models) are not able to produce strong enough clustering without the addition of a large population of ``orphan'' galaxies.  We show that rank ordering (sub-)haloes by $M_{\rm peak}$ significantly under-predicts clustering, consistent with previous results \citep[e.g.][]{Reddick:2013gi}.  In addition, more complex SHAM models which allow for evolution in the SMHM relation, e.g. M13, B13, and Y12, continue to under-predict clustering, often to a greater degree.  Each of these mass based models can be made to be consistent with SDSS clustering measurements, but only after it is assumed that about half of all sub-haloes in simulations are missing at z=0 and thus provides a motivation for a large population of orphan galaxies. Currently, there is little empirical evidence to suggest this is the case.

Beyond adding a large population of ``orphan'' galaxies, we show two modifications to SHAM models based on $M_{\rm peak}$ that can increase the clustering signal.  First, satellite galaxies may continue to grow after accretion similarly to central galaxies for some time before quenching.  Within the SHAM framework, we model satellite growth by extending sub-halo mass growth into the future by using average mass accretion histories of host-haloes before assigning stellar mass.  We show that while continued satellite growth does increase the clustering within SHAM models, even maximal growth (continued satellite growth till z=0) is not able to increase clustering sufficiently to match observations.

We show that galaxy assembly bias can increase clustering in mass based SHAM models.  In this model, earlier forming (sub-)haloes host more massive galaxies.  We find that such a model must contain two features.  First, the strength of the galaxy assembly bias must decrease towards high mass haloes.  Second, the scatter in the SMHM relation must increase towards lower masses.  Both of these features maximize the effect in low mass haloes, while minimizing it in high mass haloes where there is no issue in matching clustering observations.  However, we are not able to build a self-consistent evolving SHAM model with strong enough assembly bias to match clustering observations.

@@

Here we describe an algorithm to degrade the ordering of two variables, $X$ and $Y$, each of length $n$.  To begin with a positive correlation, each variable is placed in rank order:  
%
\begin{linenomath}
\begin{align}
X^{\prime} &= {\rm RANK}(X,X) \nonumber \\
Y^{\prime} &= {\rm RANK}(Y,Y) 
\end{align}
\end{linenomath}
%
where the ${\rm RANK(A,B)}$ operator sorts $A$ by the rank order values of $B$.  It should be noted that to begin with a negative correlation between $X$ and $Y$, $X^{\prime}$ would be put in inverse rank order, i.e. $X^{\prime} = {\rm RANK}(X,-X)$.  Next, a new variable, $Q$, is calculated for $X^{\prime}$ from the ranks by adding a normal random variable to each rank:   
%
\begin{linenomath}
\begin{equation}
q_i = n^{x^{\prime}}_i + \mathcal{N}(0, \sigma_q \times n)
\end{equation}
\end{linenomath}
%
where $\sigma_q$ is approximately the standard deviation of the change in the order relative to the length of $n$.  $X^{\prime}$ can then be re-ordered by $Q$:
%
\begin{linenomath}
\begin{equation}
X^{\prime\prime}  = {\rm RANK}(X^{\prime}, Q)
\end{equation}
\end{linenomath}
%
Henceforth, we will refer to these two variables with transformed ordering simply as $X$ and $Y$.  As an example, let $X$ and $Y$ both be uniform random variables between $[0,1]$ of length, $n=10^3$.  The relation between $X$ and $Y$ with a degraded rank order correlation characterized by $\sigma_q=0, 0.05, {\rm and}~ 0.15$ is shown in Fig. \ref{fig:xy_scatter}.  Increasing $\sigma_q$ generally result in a lower $\rho_{X,Y}$.

However, this method is inherently random in nature, and given a value of $\sigma_q$, the rank order correlation between $X$ and $Y$ will vary depending on the size of the data sets.  In Fig. \ref{fig:rho_sigma} we examined the relation between the correlation coefficient, $\rho_{XY}$, and $\sigma_q$ for two uniform random variables of length $n=10^{3}$.  For each value of $\sigma_q$ we repeat the process described above 100 times.  The error bars in Fig. \ref{fig:rho_sigma} are the standard deviation in $\rho_{XY}$ from these 100 realizations.  From this, we derive the relation between $\langle \rho_{XY} \rangle$ and $\sigma_q$, and we use this relation to choose $\sigma_q$ for a desired value of $\rho_{XY}$.  We provide an accurate fitting function for the relation given by:
%
\begin{linenomath}
\begin{align}
\label{eq:rho_fit_func}
&\langle \rho_{XY} \rangle(\sigma_q) = 1-f(\sigma_q) \\
&f(x) = \frac{1}{2}e^{-\left(\frac{x}{x_1}\right)^{\alpha}} + \frac{1}{2} \left[1+ \left( \frac{x}{x_2} \right)^{\beta} \right]^{-1} \nonumber
\end{align}
\end{linenomath}
% 
where $x_1=2/3$, $x_2=0.3$, $\alpha=-1$, and $\beta=-2$.  Furthermore, this relation is independent of the size of $X$ and $Y$ and is not affected by the distribution of values of $X$ and $Y$ since it is based on the rank ordering of $X$ and $Y$ and not the values themselves.

%
\begin{figure*}
\includegraphics[]{figures/xy_scatter_2.pdf}
\caption{The relation between two uniform random variables between [0,1] with rank scatter parameter (from left to right) $\sigma_q=0.0, 0.05, {\rm and}~ 0.15$.  $X$ and $Y$ remain highly correlated in each case with a Spearman's correlation coefficient, $\rho=1.0, 0.99, {\rm and} ~0.89$ respectively.}
\label{fig:xy_scatter}
\end{figure*}
%

>>>>

(Sub-)haloes are found using the phase-space halo finder {\tt ROCKSTAR} \citep{Behroozi:2013cn, Behroozi:2013dz}, which uses adaptive, hierarchical refinement of friends-of-friends groups in six phase-space dimensions and one time dimension. As demonstrated in \cite{Knebe:2011jc, Knebe:2013bp}, this results in a very robust tracking of (sub-)haloes \citep[also see][]{vandenBosch:2014tl}. Haloes in this catalogue are defined to be spherical volumes centred on a local density peak (SO hereafter), such that the average density inside the sphere is $\bar{\rho}_{\rm h}(z) = \Delta_{\rm vir}(z)\rho_{\rm m}(z)$.  Here $\rho_{\rm m}(z) = \Omega_{\rm m}(z) \rho_{\rm crit}(z)$, where $\rho_{\rm crit}(z) = 3H(z)^2/8\pi G$ is the critical energy density of the Universe, and $\Delta_{\rm vir}(z)$ is given by a fitting function \citep{Bryan:1998cc}:
%
\begin{linenomath}
\begin{equation}
\Delta_{\rm vir}(z) = \left[ 18\pi^2 - 82\Omega_{\Lambda}(z) - 39\Omega_{\Lambda}^2(z) \right]\Omega_m^{-1}
\end{equation}
\end{linenomath}
%
For the Bolshoi cosmology, $\Delta_{\rm vir}(z=0)\simeq 360$.  The radius of each such sphere defines the virial radius $R_{\rm vir}$ of the halo, which is related to the mass of the halo via $M_{\rm vir} = (4/3)\pi R_{\rm vir}^3\bar{\rho}_{\rm h}$. Additionally, sub-haloes in this catalogue are distinct, self-bound structures whose centre is found within the virial radius of a more massive host-halo.  For each (sub-)halo, the maximum circular velocity is defined as: $V_{\rm max} \equiv {\rm Max}[GM(<r)/r]$, where $M(<r)$ is the mass enclosed within a distance r of the (sub-)halo centre.

@@

To begin, we fit the $\langle M_* \rangle - V_{\rm peak}$ (SMVP) relation in the RV model with a function of the form:
%
\begin{linenomath}
\begin{equation}
\label{eq:smvp_relation}
\langle M_* | V_{\rm peak} \rangle = 2M_0\left(\frac{V_{\rm peak}}{V_0}\right)\left[\left(\frac{V_{\rm peak}}{V_0}\right)^{\alpha}+\left(\frac{V_{\rm peak}}{V_0}\right)^{\beta}\right]^{-1}
\end{equation}
\end{linenomath}
%
We perform a non-linear least squares fit to the mean stellar mass in 0.025 dex $V_{\rm peak}$ bins.  We find the parameters $\log(M_0/h^{-2}M_{\odot})=10.0 \pm 0.01$, $\log(V_0/{\rm km/s})=2.197 \pm 0.004$, $\alpha=-4.6 \pm 0.1$, and $\beta=-0.20 \pm 0.01$ provide an excellent fit.

As discussed, the RV model implies that galaxies grow along a fixed SMVP, i.e. galaxy growth is tied to the growth of $V_{\rm peak}$ in haloes.  Accordingly, the average growth history of galaxies is dependent on the average potential well growth histories of haloes, $\langle V_{\rm peak} \rangle (z | V_{\rm peak, 0})$, \citep[PWGHs,][]{Bosch:2014cu}, and the form of the SMVP relation, eq. \ref{eq:smvp_relation}.  We show the implied growth history of galaxies in the RV model in Fig. \ref{fig:mstar_of_z_rm} for haloes with different $V_{\rm peak}$ at z=0.0.  For comparison, we also show the stellar mass growth histories from M13, which depends on the average mass accretion histories (MAHs) of haloes, where halo mass has been converted to $V_{\rm peak}$ using eq. \ref{eq:vpeak} to place these histories on the same figure.  B13 and Y12 result in qualitatively similar growth histories as M13.

@@

\begin{figure}
    \includegraphics{figures/smhm_assem_bias.pdf}
    \caption{In the upper panel, we plot the SMHM relation for individual galaxies as points, colour-coded by the formation redshift, $z_{0.5}$.  The mean relation is plotted as a solid line with the $\pm 1\sigma$ scatter shown as dashed lines.  In the bottom panel, we show the strength of assembly bias, parametrized by the $\rho$ parameter.}
    \label{fig:assem_bias_smhm}
\end{figure}

@@

\subsection{Rank Order SHAM Assembly Bias}

@@

\subsection{Evolving SHAM Assembly Bias}

@@

%\section{Discussion}

%Each of the modifications to SHAM considered in this paper increase the clustering signal by increasing the satellite fraction.  Adding orphan galaxies increases the number of satellites, but does not change the relation between halo mass and stellar mass.  The other two solutions considered here alter the SMHM relation for satellites by 1.) allowing satellites to grow after being accreted, and 2.) allowing galaxies which become satellites to grow more massive before accretion.  By increasing the stellar mass fraction of sub-haloes, the satellite fraction increases simply because the sub-halo fraction increases as halo mass decreases.

%The tension between fitting the stellar mass function at multiple redshifts and galaxy clustering has been hinted at in many other works.  In \cite{Yang:2012ew}, when fitting galaxy clustering observations, or the conditional stellar mass function (CSMF), the data strong prefers more massive satellites and longer sub-halo survival times.  It is only when we apply this model (Y12) to dark matter simulations directly, that it becomes clear that there simply aren't enough extant sub-haloes.  \citep{Lim:2016ul} find a similar result, but instead of fitting to $w_p(r_p)$, they compare to the CSMF only.  Again, only models which allow for a significant orphan population can provide a good fit the the faint end of the CSMF, another indication that the true culprit in the clustering crisis is a lack of satellite galaxies.

%Broadly, the usefulness of orphans when fitting galaxy clustering is well established.  \cite{Pujol:2017ua}, in a comparison of many galaxy formation models, find that only models with orphan galaxies are able to fit clustering observations on small scales.

%{\bf [Effect of baryons on sub-haloes]}

%{\bf [Methods to track sub-haloes that are robust to artificial merging/disruption]}

%Most bound halo particle \citep{Hong:2016hv}.

%{\bf [Assembly Bias]}
%\citep{Zentner:2016tz} find significant evidence for assembly bias {\bf [is this still true?]} in low luminosity samples, exactly the regime where clustering is under-predicted.   
%The assumptions in SHAM have been independently examined in the Eagle simulation by \cite{Matthee:2016vm}, who find that at fixed halo mass, the scatter in the SMHM relation is correlated with formation time.

%{\bf [discussion of Vmax vs Mvir as indicators of stellar mass]}

%Most studies which tout $V_{\rm max}$ as a superior halo property for SHAM do so when fitting galaxy clustering at z=0 \citep{Reddick:2013gi, Lehmann:2015vi}.  \cite{Matthee:2016vm} find that scatter is minimized in the $V_{\rm max}$-$M_*$ relation compared to the SMHM relation.

%{\bf [Observational tests to distinguish between solutions proposed here]}

%Differentiating between the solutions discussed in this work may prove to be difficult, especially if each plays some role.  Observations to constrain the SMHM relation for satellite galaxies are difficult.  \cite{Niemiec:2017ul} use weak lensing to examine the SMHM relation in cluster sub-haloes.

\section{Discussion \& Summary}

We have shown that there is no published sub-halo abundance matching (SHAM) model that simultaneously:
\begin{enumerate}
\item fits the stellar mass function as a function of redshift, $\phi(M_*,z)$,
\item fits the clustering of galaxies at z=0, $w_p(r_p)$,
\item and uses only identified, extant, sub-haloes in high resolution dark matter simulations.
\end{enumerate}
Models that fit observations of galaxy clustering are incompatible with the observed evolution of the stellar mass function and expectations for the build up of stellar mass in haloes.  Conversely, SHAM models which self-consistently fit the stellar mass function as it evolves significantly under-predict galaxy clustering signals at small scales ($\leq 1 h^{-1}{\rm Mpc}$).  This tension exposes a clustering ``crisis'' for SHAM.

Of the five different SHAM models examined in this work, only SHAM based on rank ordering (sub-)haloes by peak maximum circular velocity, $V_{\rm peak}$, (RV  model) results in a robust galaxy clustering signal consistent with observations.  This finding is in-line with previous work that finds $V_{\rm peak}$ is the best quantity to consider when fitting galaxy clustering observations \citep{Reddick:2013gi, Lehmann:2015vi}.  However, an implicit assumption in $V_{\rm peak}$ SHAM is that the stellar mass-$V_{\rm peak}$ (SMVP) relation does not evolve. Because haloes grow their potential wells early \citep[e.g.][]{Bosch:2014cu}, a non-evolving SMVP relation results in haloes building up stellar mass too early.

SHAM models based on peak halo mass, $M_{\rm peak}$, (RM, M13, B13, and Y12 models) do not produce strong enough clustering signals with respect to observations, especially on small scales, without modification.  We have examined three modifications to mass based SHAM models that alleviate the clustering crisis to varying degrees: the addition of orphan galaxies, stellar mass growth post-accretion for satellites, and assembly bias.  Each of these ``solutions'' addresses the clustering crisis by increasing the number of satellite galaxies.

The demand for increasing the number of satellites has been found in my other studies.  In the original semi-analytic implementation of the Y12 model, \cite{Yang:2012ew} find a need for more massive satellites and longer sub-halo survival times than traditional SHAM implementations.  It is only when we apply the Y12 model to dark matter simulations directly, that it becomes clear that there simply aren't enough extant sub-haloes to fit the clustering observations.  \citep{Lim:2016ul} find a similar result when fitting the conditional stellar mass function (CSMF).  Again, only models which allow for a significant orphan population can provide a good fit the the faint end of the CSMF, another indication that the true culprit in the clustering crisis is a lack of satellite galaxies.  Furthermore, this is not a problem unique to SHAM, \cite{Pujol:2017ua}, in a comparison of many galaxy formation models, find that only models with orphan galaxies are able to fit clustering observations on small scales.

While the need for orphan galaxies is well established, the motivation for the missing sub-haloes associated with orphan galaxies in high resolution simulations is lacking.  While the mass resolution of simulations places an absolute limit on their ability to resolve highly stripped sub-haloes, we find no empirical evidence of missing sub-haloes.  By examining the power-law behaviour of the sub-halo fraction, we find that the resolution of the Bolshoi simulation, $m_{\rm p} = 1.35 \times 10^8 \msunh$, appears to be sufficient to model SDSS-like galaxy samples ($M_* \geq ~h^{-2}M_{\odot}$), where the majority of satellite galaxies live in haloes with peak masses $\gtrsim 1000 \times m_p$, consistent with an independent analysis by \citep{Guo:2013fm}.  Despite the lack of evidence, we find that mass based SHAM models require approximately half of satellites are orphans to fit galaxy clustering observations.  This large fraction of orphan galaxies is similar to the number required by \cite{Yang:2012ew}.

The appeal of SHAM is to leverage the statistical power of large dark matter only (DMO) simulations.  However, DMO simulations may not be reliable to resolve substructure where baryons and the astrophysics of galaxy evolution may significantly modify the abundance, distribution, and structure of sub-haloes.

It has been suggested that the inclusion of baryons in cosmological simulations may more tightly bind substructure and therefore increase the survival time of sub-haloes.

baryons keep sub-haloes via baryonic contraction \citep{Fiacconi:2016ba}

  Baryons destroy sub-haloes \citep{Brooks:2014jv} \citep{Read:2006da, Read:2006hw} \citep{GarrisonKimmel:2017cv} \citep{Wetzel:2016iy} \citep{Despali:2016uv}

    \citep{GarrisonKimmel:2017tu} find the exact opposite trend where the disk structures depletes the abundance of sub-ahaloes by a factor of $\sim 2$ in the central regions of sub-haloes relative to dark matter only (DMO) simulations.  Since we work with only DMO simulations, we do not consider this effect; however, we note that this effect would only exasperate the clustering crisis further.

Given the uncertain contribution of orphan galaxies, we also examine two other physically motivated methods to enhance the satellite contribution in mass based SHAM models.  First, satellite galaxies may continue to grow after accretion similarly to central galaxies for some time before quenching.  Within this framework, the process(es) which quenches satellites is delayed, while in the interim satellites continue to form stars similarly to central galaxies \citep{Wetzel:2013dw}.  This idea is at odds with the assumption in many SHAM models that the stellar mass of satellites is set at $z_{\rm acc}$ and serves as a sort of fossil record of the SMHM relation at that redshift.  Continued growth after accretion generally increases the number of satellites above a given stellar mass threshold.  We find that reasonable delay times before quenching result in modest increases to the satellite fraction and, as a result, the clustering signal on small scales.  Again, Y12 find evidence for significant post-accretion evolution of stellar mass, such that satellites acquire a stellar mass that is close to that of central galaxies.  Our model for growth allows for even larger masses, but remains insufficient.  \citep{Behroozi:2015wx} apply a similar model for post-accretion growth and find consistent results when examining close galaxy pairs, but do not comment on the affect on $w_p(r_p)$.  Regardless, our results suggest post-accretion evolution of satellites is an important phenomena to model in order to reproduce the small scale clustering of galaxies, but this effect on its own is not sufficient to solve the clustering crisis in this paper.

Finally, we show that galaxy assembly bias can increase clustering in mass based SHAM models.

    In this model, earlier forming (sub-)haloes host more massive galaxies.  We find that such a model must contain two features.  First, the strength of the galaxy assembly bias must decrease towards high mass haloes.  Second, the scatter in the SMHM relation must increase towards lower masses.  Both of these features maximize the effect in low mass haloes, while minimizing it in high mass haloes where there is no issue in matching clustering observations.  However, we are not able to build a self-consistent evolving SHAM model with strong enough assembly bias to match clustering observations.

@@

Here we describe an algorithm to degrade the ordering of two variables, $X$ and $Y$, each of length $n$.  To begin with a positive correlation, each variable is placed in rank order:  
%
\begin{linenomath}
\begin{align}
X^{\prime} &= {\rm RANK}(X,X) \nonumber \\
Y^{\prime} &= {\rm RANK}(Y,Y) 
\end{align}
\end{linenomath}
%
where the ${\rm RANK(A,B)}$ operator sorts $A$ by the rank order values of $B$.  It should be noted that to begin with a negative correlation between $X$ and $Y$, $X^{\prime}$ would be put in inverse rank order, i.e. $X^{\prime} = {\rm RANK}(X,-X)$.  Next, a new variable, $Q$, is calculated for $X^{\prime}$ from the ranks by adding a normal random variable to each rank:   
%
\begin{linenomath}
\begin{equation}
q_i = n^{x^{\prime}}_i + \mathcal{N}(0, \sigma_q \times n)
\end{equation}
\end{linenomath}
%
where $\sigma_q$ is approximately the standard deviation of the change in the order relative to the length of $n$.  $X^{\prime}$ can then be re-ordered by $Q$:
%
\begin{linenomath}
\begin{equation}
X^{\prime\prime}  = {\rm RANK}(X^{\prime}, Q)
\end{equation}
\end{linenomath}
%
Henceforth, we will refer to these two variables with transformed ordering simply as $X$ and $Y$.  %As an example, let $X$ and $Y$ both be uniform random variables between $[0,1]$ of length, $n=10^3$.  The relation between $X$ and $Y$ with a degraded rank order correlation characterized by $\sigma_q=0, 0.05, {\rm and}~ 0.15$ is shown in Fig. \ref{fig:xy_scatter}.  Increasing $\sigma_q$ generally result in a lower $\rho_{X,Y}$.

This method is inherently random in nature, and given a value of $\sigma_q$, the rank order correlation between $X$ and $Y$ will vary depending on the size of the data sets.  In Fig. \ref{fig:rho_sigma} we examined the relation between the correlation coefficient, $\rho_{XY}$, and $\sigma_q$ for two uniform random variables of length $n=10^{3}$.  For each value of $\sigma_q$ we repeat the process described above 100 times.  The error bars in Fig. \ref{fig:rho_sigma} are the standard deviation in $\rho_{XY}$ from these 100 realizations.  From this, we derive the relation between $\langle \rho_{XY} \rangle$ and $\sigma_q$, and we use this relation to choose $\sigma_q$ for a desired value of $\rho_{XY}$.  We provide an accurate fitting function for the relation given by:
%
\begin{linenomath}
\begin{align}
\label{eq:rho_fit_func}
&\langle \rho_{XY} \rangle(\sigma_q) = 1-f(\sigma_q) \\
&f(x) = \frac{1}{2}e^{-\left(\frac{x}{x_1}\right)^{\alpha}} + \frac{1}{2} \left[1+ \left( \frac{x}{x_2} \right)^{\beta} \right]^{-1} \nonumber
\end{align}
\end{linenomath}
% 
where $x_1=2/3$, $x_2=0.3$, $\alpha=-1$, and $\beta=-2$.  Furthermore, this relation is independent of the size of $X$ and $Y$ and is not affected by the distribution of values themselves since it is based on the rank ordering.

%
%\begin{figure*}
%\includegraphics[]{figures/xy_scatter_2.pdf}
%\caption{The relation between two uniform random variables between [0,1] with rank scatter parameter (from left to right) $\sigma_q=0.0, 0.05, {\rm and}~ 0.15$.  $X$ and $Y$ remain highly correlated in each case with a Spearman's correlation coefficient, $\rho=1.0, 0.99, {\rm and} ~0.89$ respectively.}
%\label{fig:xy_scatter}
%\end{figure*}
%
